\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs

### 2020-06-08 main.tex
Small adjustments here and there, 4 pages.

\xhdr{Synthetic.}
We also provide several synthetic graph datasets to demonstrate the strengths or weaknesses of specific methods. The datasets \textsc{SyntheticNew} and \textsc{SyntheticNew} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes. \citet{Knyazev2019} introduced the datasets \textsc{Colors} and \textsc{Triangles}, where the task is to count the number of nodes with a given one-hot-encoded color and the number of triangles, respectively.

@@

For \textsc{Zinc}, we used the given train, validation split, test split, and report the MAE over the test set. For the \textsc{Alchemy} and \textsc{QM9} datasets, we uniformly and at random sampled 80\% of the graphs for training, and 10\% for validation and testing, respectively. Moreover, following~\cite{Che+2020,Gil+2017}, we normalized the targets of the training split to zero mean and unit variance. We used a single model to predict all targets. Following~\cite{Kli+2020}, we report mean standardized MAE and mean standardized logMAE. We repeated each experiment five times (with different random splits in case of \textsc{Alchemy} and \textsc{QM9}) and report average scores and standard deviations.  Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$ with a starting learning rate of $0.001$ and a minimum of $10^{-6}$.

>>>>

\xhdr{Synthetic.}
We also provide several synthetic graph datasets to demonstrate the strengths or weaknesses of specific methods. The datasets \textsc{Synthetic} and \textsc{SyntheticNew} were created by \citet{Fer+2013} (see Erratum) and \citet{Mor+2016}, respectively, to demonstrate the ability of kernels to operate on graphs with continuous attributes. \citet{Knyazev2019} introduced the datasets \textsc{Colors} and \textsc{Triangles}, where the task is to count the number of nodes with a given one-hot-encoded color and the number of triangles, respectively.

@@

For \textsc{Zinc}, we used the given train, validation split, test split, and report the MAE over the test set. For the \textsc{Alchemy} and \textsc{QM9} datasets, we uniformly and at random sampled 80\% of the graphs for training, and 10\% for validation and testing, respectively. Moreover, following~\cite{Che+2020,Gil+2017}, we normalized the targets of the training split to zero mean and unit variance. We used a single model to predict all targets. Following~\cite{Kli+2020}, we report mean standardized MAE and mean standardized logMAE. We repeated each experiment five times (with different random splits in case of \textsc{Alchemy} and \textsc{QM9}) and report average scores and standard deviations.  Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$, and a starting learning rate of $0.001$ with a minimum of $10^{-6}$.
